Enhancement of SDR in Thessaloniki

### 2024-06-06 GHI_enh_04_investigate.tex
Commit 2024-06-06 11:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-05}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Attaching package: 'zoo'
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:data.table':

    yearmon, yearqtr
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:base':

    as.Date, as.Date.numeric
\end{verbatim}

\begin{verbatim}
Registered S3 methods overwritten by 'ggpp':
  method                  from   
  heightDetails.titleGrob ggplot2
  widthDetails.titleGrob  ggplot2
\end{verbatim}

\begin{verbatim}
Attaching package: 'ggpp'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:ggh4x':

    stat_centroid
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:ggplot2':

    annotate
\end{verbatim}

\begin{verbatim}
Registered S3 method overwritten by 'ggpmisc':
  method                  from   
  as.character.polynomial polynom
\end{verbatim}

\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

@@

@@

@@

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_daily-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_week-1} \end{center}

@@

\begin{verbatim}
2024-06-05 17:31:25.4 athan@tyler GHI_enh_04_investigate.R 1.589891 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-06}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

\hypertarget{climatolgy}{%
\section{Climatolgy}\label{climatolgy}}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-MW-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N_MW-1} \end{center}

\hypertarget{monthly-ce}{%
\subsection{Monthly CE}\label{monthly-ce}}

@@

\hypertarget{monthly-weighted-ce}{%
\subsection{Monthly weighted CE}\label{monthly-weighted-ce}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N_MW-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N_MW-2} \end{center}

\hypertarget{monthly-extreme-ce-raw}{%
\subsection{Monthly extreme CE raw}\label{monthly-extreme-ce-raw}}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-MW-1} \end{center}

\hypertarget{monthly-extreme-ce}{%
\subsection{Monthly extreme CE}\label{monthly-extreme-ce}}

@@

\hypertarget{monthly-weighted-extreme-ce}{%
\subsection{Monthly weighted extreme CE}\label{monthly-weighted-extreme-ce}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N_MW-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N_MW-2} \end{center}

@@

\begin{verbatim}
2024-06-06 08:05:21.1 athan@tyler GHI_enh_04_investigate.R 2.110215 mins
\end{verbatim}
